Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
cleaned up inline citations

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \cite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependent-based SParseval measure
\cite{roark06:sparseval}, originally designed as a parse-quality
metric for speech, is a similar approach, in that it is an F-measure
over a decomposition of reference and hypothesis trees.
\cite{owczarzak07labelleddepseval}'s \textbf{d} and \textbf{d\_var}
measures compare LFG-derived relational tuples from reference and
hypothesis translations and report substantial improvement in
correlation with human judgment relative to BLEU and TER.

These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. Some \cite{liu05syntaxformteval,roark06:sparseval} use
PCFG parsers with deterministic head-finding, while others
\cite{owczarzak07labelleddepseval}extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\cite{roark06:sparseval,owczarzak07labelleddepseval} using a
widely-used and publically available PCFG parser and deterministic
head-finding rules.

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \cite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

@@

This work explores a family of dependency pair match (DPM) measures
that are composed of precision and recall combinations over various
decompositions of a syntactic dependency tree. These measures are
extensions of the dependency-pair F measures found in
\cite{roark06:sparseval,owczarzak07labelleddepseval}.  Rather than
comparing string sequences, as BLEU does with its $n$-gram precision,
this approach defers to a parser for an indication of the relevant
words that indicate more about its meaning --- in these
implementations, the head on which that word depends.  Each sentence
(both reference and hypothesis) is converted to a labeled syntactic
dependency tree and then relations from each tree are extracted and
compared.

@@

When multiple decomposition types used together, we may combine these
subscores in a variety of ways.  We may compute precision and recall
subscores for each decomposition separately, or, since the results of
each decomposition are of different types entirely, we may compute
them as members of one large bag for an even simpler F score.  These
two approaches are equivalent when only one decomposition type is
included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
Dependency-based SParseval and Owczarzak \textit{et al.}'s
\cite*{owczarzak07labelleddepseval} \textbf{d} approach, then, may
each be understood as $F[dlh]$, while the latter's \textbf{d\_var}
method may be understood as something close to $F[dl,lh]$.

@@

%
In this work, we use a state-of-the-art PCFG (the first stage of
\cite{charniak-johnson:2005:ACL}) and context-free head-finding rules
\cite{magerman95headfinding} to generate a 50-best list of dependency
trees for each hypothesis and reference translation.  We use the
parser's default (English-language) Wall Street Journal training
parameters.  Head-finding uses the Charniak parser's rules, with three
modifications: prepositional and complementizer phrases choose nominal
and verbal heads respectively (rather than functional heads) and
auxiliary verbs are modifiers of main verbs (rather than the
converse).

Having constructed the dependency tree, we label the arcs as $d
\stackrel{A/B}{\to} h$, where the arc label $A/B$ between dependent
$d$ and its head $h$ is composed of $A$ (the lowest constituent-label
headed by $h$ and dominating $d$) and $B$ (the highest constituent
label headed by $d$). 
\begin{figure}
  % \centering
  \Tree
  [.\headlabel{S}{stumbled}
    [.\headlabel{NP}{cat}
      [.\headlabel{DT}{the} the ]
      [.\headlabel{NN}{cat} cat ]
    ]
    [.\headlabel{VP}{stumbled} 
      [.\headlabel{VBD}{stumbled} stumbled ]
    ]
  ]
  \\
  \begin{center}
    \includegraphics[scale=0.6]{dpm-example-depextract.eps}
  \end{center}
  \caption{An example constituent tree (heads of each constituent are
    listed small below the label) and the labelled dependency tree
    derived from it using the strategy described in
    section~\ref{sec:paradigm}.}
  \label{fig:depextract}
\end{figure}
For example, in figure~\ref{fig:depextract}, the S node is the
lowest node headed by \emph{stumbled} that dominates \emph{cat}, and
the NP node is the highest constituent label headed by \emph{cat}, so
the arc between \emph{cat} and \emph{stumbled} is labelled \arclabel{S/NP}.
%
This strategy is very similar to one adopted in the reference
implementation of labelled-dependency \textsc{SParseval}, and may be
considered as an approximation of the rich semantics generated by
\cite{cahill04lfg} or another heavily knowledge-engineered
parser, but with much less knowledge-engineering required.

@@

    \cite{owczarzak07labelleddepseval} report no use of parse weights,

@@

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\footnote{Our segment
  count differs from \cite{owczarzak07labelleddepseval}, who report
  16,800 segments over the same corpus. We find baseline correlations
  (BLEU$_4$ and TER) lower than those reported there as well, so the
  results presented here are not directly comparable with that paper,
  though we demonstrate similar gains over those baselines in
  essentially the same corpus. % (section~\ref{sec:facorr:newdeps}).}
}
comparison with \cite{owczarzak07labelleddepseval}, we treat each
judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\footnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.

>>>>

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \inlinecite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependent-based SParseval measure
\cite{roark06:sparseval}, originally designed as a parse-quality
metric for speech, is a similar approach, in that it is an F-measure
over a decomposition of reference and hypothesis trees.
\inlinecite{owczarzak07labelleddepseval} proposed \textbf{d} and
\textbf{d\_var} measures that compare LFG-derived relational tuples
from reference and hypothesis translations and reported substantial
improvement in correlation with human judgment relative to BLEU and
TER.

These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. Some \cite{liu05syntaxformteval,roark06:sparseval} use
PCFG parsers with deterministic head-finding, while others
\cite{owczarzak07labelleddepseval} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{roark06:sparseval,owczarzak07labelleddepseval} using a
widely-used and publically available PCFG parser and deterministic
head-finding rules.

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \inlinecite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we explore both kinds of
evaluation.

@@

This work explores a family of dependency pair match (DPM) measures
that are composed of precision and recall combinations over various
decompositions of a syntactic dependency tree. These measures are
extensions of the dependency-pair F measures found in
\inlinecite{roark06:sparseval,owczarzak07labelleddepseval}.  Rather than
comparing string sequences, as BLEU does with its $n$-gram precision,
this approach defers to a parser for an indication of the relevant
words that indicate more about its meaning --- in these
implementations, the head on which that word depends.  Each sentence
(both reference and hypothesis) is converted to a labeled syntactic
dependency tree and then relations from each tree are extracted and
compared.

@@

When multiple decomposition types used together, we may combine these
subscores in a variety of ways.  We may compute precision and recall
subscores for each decomposition separately, or, since the results of
each decomposition are of different types entirely, we may compute
them as members of one large bag for an even simpler F score.  These
two approaches are equivalent when only one decomposition type is
included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
Dependency-based SParseval and the \textbf{d} approach from
\inlinecite{owczarzak07labelleddepseval}, then, may
each be understood as $F[dlh]$, while the latter's \textbf{d\_var}
method may be understood as something close to $F[dl,lh]$.

@@

%
In this work, we use a state-of-the-art PCFG (the first stage of
\inlinecite{charniak-johnson:2005:ACL}) and context-free head-finding rules
\cite{magerman95headfinding} to generate a 50-best list of dependency
trees for each hypothesis and reference translation.  We use the
parser's default (English-language) Wall Street Journal training
parameters.  Head-finding uses the Charniak parser's rules, with three
modifications: prepositional and complementizer phrases choose nominal
and verbal heads respectively (rather than functional heads) and
auxiliary verbs are modifiers of main verbs (rather than the
converse).

Having constructed the dependency tree, we label the arcs as $d
\stackrel{A/B}{\to} h$, where the arc label $A/B$ between dependent
$d$ and its head $h$ is composed of $A$ (the lowest constituent-label
headed by $h$ and dominating $d$) and $B$ (the highest constituent
label headed by $d$). 
\begin{figure}
  % \centering
  \Tree
  [.\headlabel{S}{stumbled}
    [.\headlabel{NP}{cat}
      [.\headlabel{DT}{the} the ]
      [.\headlabel{NN}{cat} cat ]
    ]
    [.\headlabel{VP}{stumbled} 
      [.\headlabel{VBD}{stumbled} stumbled ]
    ]
  ]
  \\
  \begin{center}
    \includegraphics[scale=0.6]{dpm-example-depextract.eps}
  \end{center}
  \caption{An example constituent tree (heads of each constituent are
    listed small below the label) and the labelled dependency tree
    derived from it using the strategy described in
    section~\ref{sec:paradigm}.}
  \label{fig:depextract}
\end{figure}
For example, in figure~\ref{fig:depextract}, the S node is the
lowest node headed by \emph{stumbled} that dominates \emph{cat}, and
the NP node is the highest constituent label headed by \emph{cat}, so
the arc between \emph{cat} and \emph{stumbled} is labelled \arclabel{S/NP}.
%
This strategy is very similar to one adopted in the reference
implementation of labelled-dependency \textsc{SParseval}, and may be
considered as an approximation of the rich semantics generated by LFG
parsers \cite{cahill04lfg} or another heavily knowledge-engineered
parser, but with much less knowledge-engineering required.

@@

    \inlinecite{owczarzak07labelleddepseval} report no use of parse weights,

@@

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\footnote{Our segment
  count differs from \inlinecite{owczarzak07labelleddepseval}, who report
  16,800 segments over the same corpus. We find baseline correlations
  (BLEU$_4$ and TER) lower than those reported there as well, so the
  results presented here are not directly comparable with that paper,
  though we demonstrate similar gains over those baselines in
  essentially the same corpus. % (section~\ref{sec:facorr:newdeps}).}
}
comparison with \inlinecite{owczarzak07labelleddepseval}, we treat each
judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\footnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.
